Equivalent Income Outcome Visualisation - Batch out

### 2023-09-12 minos/outcomes/equivalent_income_out.Rmd
Changed loneliness to string var from numeric so its easier to understand. Also lots of changes to EI plots

```{r}
# set output path to SIPHER 7 experiment out
out.path <- here::here('output', 'SIPHER7/')
# read all files into dataframe (util function handles runtime subdirectory etc.)
base.dat <- read_singular_local_out(out.path, 'baseline', drop.dead = TRUE)
allchild.dat <- read_singular_local_out(out.path, 'hhIncomeChildUplift', drop.dead = TRUE)
pov.dat <- read_singular_local_out(out.path, 'hhIncomePovertyLineChildUplift', drop.dead = TRUE)
wage.dat <- read_singular_local_out(out.path, 'livingWageIntervention', drop.dead = TRUE)
energy.dat <- read_singular_local_out(out.path, 'energyDownlift', drop.dead = TRUE)
```

@@

```{r}
base.dat <- filter(base.dat, time > 2020)
allchild.dat <- filter(allchild.dat, time > 2020)
pov.dat <- filter(pov.dat, time > 2020)
wage.dat <- filter(wage.dat, time > 2020)
energy.dat <- filter(energy.dat, time > 2020)
```

@@

```{r}
equivalent_income_comparison_fullpop(base.dat, allchild.dat, 'allChild')
equivalent_income_comparison_fullpop(base.dat, pov.dat, 'povertyChild')
equivalent_income_comparison_fullpop(base.dat, wage.dat, 'LivingWage')
equivalent_income_comparison_fullpop(base.dat, energy.dat, 'EnergyDownlift')
```

@@

allchild.subset <- allchild.dat %>%
  select(pidp, time, equivalent_income, alive, weight) %>%
  filter(alive != 'dead') %>%
  group_by(time) %>%
  summarise(equivalent_income = weighted.mean(equivalent_income, w = weight))
allchild.subset$scenario <- 'AllChild'

pov.subset <- pov.dat %>%
  select(pidp, time, equivalent_income, alive, weight) %>%
  filter(alive != 'dead') %>%
  group_by(time) %>%
  summarise(equivalent_income = weighted.mean(equivalent_income, w = weight))
pov.subset$scenario <- 'PovertyChild'

wage.subset <- wage.dat %>%
  select(pidp, time, equivalent_income, alive, weight) %>%
  filter(alive != 'dead') %>%
  group_by(time) %>%
  summarise(equivalent_income = weighted.mean(equivalent_income, w = weight))
wage.subset$scenario <- 'LivingWage'

@@

all.combined <- rbind(base.subset, allchild.subset, pov.subset, wage.subset, energy.subset)
all.combined$scenario <- factor(all.combined$scenario, levels = c('Baseline', 'AllChild', 'PovertyChild', 'LivingWage', 'EnergyDownlift'))

@@

```{r}
equivalent_income_comparison_treated(base.dat, allchild.dat, 'allChild')
equivalent_income_comparison_treated(base.dat, pov.dat, 'povertyChild')
equivalent_income_comparison_treated(base.dat, wage.dat, 'LivingWage')
equivalent_income_comparison_treated(base.dat, energy.dat, 'EnergyDownlift')
```

@@

```{r, include=FALSE}
# THink about this...
# We can use the income_boosted and boost_amount variables to remove the income boost from people and visualise that

base.sub2 <- base.dat %>%
  select(pidp, time, equivalent_income, alive) %>%
  filter(alive != 'dead') %>%
  select(-alive) %>%
  rename(baseline = equivalent_income)

allchild.sub2 <- allchild.dat %>%
  select(pidp, time, equivalent_income, income_boosted, boost_amount, alive) %>%
  filter(alive != 'dead') %>%
  select(-alive) %>%
  rename(allchild = equivalent_income)

allchild.merged <- merge(base.sub2, allchild.sub2, by = c('pidp', 'time'))

boosted.pidps <- allchild.sub2 %>%
  filter(income_boosted == 'True') %>%
  select(pidp)

allchild.boosted <- allchild.merged %>%
  filter(pidp %in% boosted.pidps$pidp) %>%
  filter(income_boosted == 'True' | time == 2020) %>%
  mutate(adjusted_EI = allchild - boost_amount) %>%
  select(-allchild, -income_boosted, -boost_amount) %>%
  group_by(time) %>%
  summarise(baseline = mean(baseline),
            allchild_adj = mean(adjusted_EI)) %>%
  pivot_longer(cols = baseline:allchild_adj,
               names_to = 'scenario',
               values_to = 'equivalent_income')
```

```{r}
ggplot(data = allchild.boosted, aes(x = time, y = equivalent_income, group = scenario, color = scenario)) +
  geom_line()
```

@@

int.inc <- wage.dat %>%
  select(pidp, time, hh_income, equivalent_income, weight) %>%
  group_by(time) %>%
  summarise(hh_income = weighted.mean(hh_income, w = weight, na.rm = TRUE),
            equivalent_income = weighted.mean(equivalent_income, w = weight, na.rm = TRUE)) %>%
  mutate(source = 'Living_Wage')

@@

income_equivinc_change(base.dat, energy.dat)
income_equivinc_change(base.dat, wage.dat)
```

@@

```{r}
## just look at means in case the means are causing some problems
base.dat.2 <- base.dat
base.dat.2$S7_housing_quality2[base.dat.2$S7_housing_quality == 'No to all'] <- 1
base.dat.2$S7_housing_quality2[base.dat.2$S7_housing_quality == 'Yes to some'] <- 2
base.dat.2$S7_housing_quality2[base.dat.2$S7_housing_quality == 'Yes to all'] <- 3
wage.dat.2 <- energy.dat
wage.dat.2$S7_housing_quality2[wage.dat.2$S7_housing_quality == 'No to all'] <- 1
wage.dat.2$S7_housing_quality2[wage.dat.2$S7_housing_quality == 'Yes to some'] <- 2
wage.dat.2$S7_housing_quality2[wage.dat.2$S7_housing_quality == 'Yes to all'] <- 3

base.hous.mean <- base.dat.2 %>%
  select(pidp, time, S7_housing_quality2, weight) %>%
  group_by(time) %>%
  summarise(mean_housing = weighted.mean(S7_housing_quality2, w = weight, na.rm = TRUE)) %>%
  mutate(source = 'Baseline')
wage.hous.mean <- wage.dat.2 %>%
  select(pidp, time, S7_housing_quality2, weight) %>%
  group_by(time) %>%
  summarise(mean_housing = weighted.mean(S7_housing_quality2, w = weight, na.rm = TRUE)) %>%
  mutate(source = 'EnergyCrisis')

combined <- rbind(base.hous.mean, wage.hous.mean)

ggplot(combined, aes(x = time, y = mean_housing, group = source, color = source)) +
  geom_line() +
  geom_point()
```

>>>>

```{r}
# set output path to SIPHER 7 experiment out
out.path <- here::here('output', 'SIPHER7/')
# read all files into dataframe (util function handles runtime subdirectory etc.)
base.dat <- read_singular_local_out(out.path, 'baseline', drop.dead = TRUE)
# allchild.dat <- read_singular_local_out(out.path, 'hhIncomeChildUplift', drop.dead = TRUE)
# pov.dat <- read_singular_local_out(out.path, 'hhIncomePovertyLineChildUplift', drop.dead = TRUE)
# wage.dat <- read_singular_local_out(out.path, 'livingWageIntervention', drop.dead = TRUE)
energy.dat <- read_singular_local_out(out.path, 'energyDownlift', drop.dead = TRUE)
```

@@

```{r}
base.dat <- filter(base.dat, time > 2020)
# allchild.dat <- filter(allchild.dat, time > 2020)
# pov.dat <- filter(pov.dat, time > 2020)
# wage.dat <- filter(wage.dat, time > 2020)
energy.dat <- filter(energy.dat, time > 2020)
```

@@

```{r}
# equivalent_income_comparison_fullpop(base.dat, allchild.dat, 'allChild')
# equivalent_income_comparison_fullpop(base.dat, pov.dat, 'povertyChild')
# equivalent_income_comparison_fullpop(base.dat, wage.dat, 'LivingWage')
equivalent_income_comparison_fullpop(base.dat, energy.dat, 'EnergyDownlift')
```

@@

# allchild.subset <- allchild.dat %>%
#   select(pidp, time, equivalent_income, alive, weight) %>%
#   filter(alive != 'dead') %>%
#   group_by(time) %>%
#   summarise(equivalent_income = weighted.mean(equivalent_income, w = weight))
# allchild.subset$scenario <- 'AllChild'
# 
# pov.subset <- pov.dat %>%
#   select(pidp, time, equivalent_income, alive, weight) %>%
#   filter(alive != 'dead') %>%
#   group_by(time) %>%
#   summarise(equivalent_income = weighted.mean(equivalent_income, w = weight))
# pov.subset$scenario <- 'PovertyChild'
# 
# wage.subset <- wage.dat %>%
#   select(pidp, time, equivalent_income, alive, weight) %>%
#   filter(alive != 'dead') %>%
#   group_by(time) %>%
#   summarise(equivalent_income = weighted.mean(equivalent_income, w = weight))
# wage.subset$scenario <- 'LivingWage'

@@

# all.combined <- rbind(base.subset, allchild.subset, pov.subset, wage.subset, energy.subset)
# all.combined$scenario <- factor(all.combined$scenario, levels = c('Baseline', 'AllChild', 'PovertyChild', 'LivingWage', 'EnergyDownlift'))

all.combined <- rbind(base.subset, energy.subset)
all.combined$scenario <- factor(all.combined$scenario, levels = c('Baseline', 'EnergyDownlift'))

@@

```{r}
# equivalent_income_comparison_treated(base.dat, allchild.dat, 'allChild')
# equivalent_income_comparison_treated(base.dat, pov.dat, 'povertyChild')
# equivalent_income_comparison_treated(base.dat, wage.dat, 'LivingWage')
equivalent_income_comparison_treated(base.dat, energy.dat, 'EnergyDownlift')
```

@@

```{r, include=FALSE}
# # THink about this...
# # We can use the income_boosted and boost_amount variables to remove the income boost from people and visualise that
# 
# base.sub2 <- base.dat %>%
#   select(pidp, time, equivalent_income, alive) %>%
#   filter(alive != 'dead') %>%
#   select(-alive) %>%
#   rename(baseline = equivalent_income)
# 
# allchild.sub2 <- allchild.dat %>%
#   select(pidp, time, equivalent_income, income_boosted, boost_amount, alive) %>%
#   filter(alive != 'dead') %>%
#   select(-alive) %>%
#   rename(allchild = equivalent_income)
# 
# allchild.merged <- merge(base.sub2, allchild.sub2, by = c('pidp', 'time'))
#   
# boosted.pidps <- allchild.sub2 %>%
#   filter(income_boosted == 'True') %>%
#   select(pidp)
# 
# allchild.boosted <- allchild.merged %>%
#   filter(pidp %in% boosted.pidps$pidp) %>%
#   filter(income_boosted == 'True' | time == 2020) %>%
#   mutate(adjusted_EI = allchild - boost_amount) %>%
#   select(-allchild, -income_boosted, -boost_amount) %>%
#   group_by(time) %>%
#   summarise(baseline = mean(baseline),
#             allchild_adj = mean(adjusted_EI)) %>%
#   pivot_longer(cols = baseline:allchild_adj,
#                names_to = 'scenario',
#                values_to = 'equivalent_income')
```

```{r}
# ggplot(data = allchild.boosted, aes(x = time, y = equivalent_income, group = scenario, color = scenario)) +
#   geom_line()
```

@@

```{r}
# base.inc <- base.dat %>%
#   select(pidp, time, hh_income, equivalent_income, weight) %>%
#   group_by(time) %>%
#   summarise(hh_income = weighted.mean(hh_income, w = weight, na.rm = TRUE),
#             equivalent_income = weighted.mean(equivalent_income, w = weight, na.rm = TRUE)) %>%
#   mutate(source = 'Baseline')
# 
# int.inc <- wage.dat %>%
#   select(pidp, time, hh_income, equivalent_income, weight) %>%
#   group_by(time) %>%
#   summarise(hh_income = weighted.mean(hh_income, w = weight, na.rm = TRUE),
#             equivalent_income = weighted.mean(equivalent_income, w = weight, na.rm = TRUE)) %>%
#   mutate(source = 'Living_Wage')
# 
# combined <- rbind(base.inc, int.inc)
# combined <- combined %>%
#   pivot_longer(cols=hh_income:equivalent_income,
#                names_to = 'income_type',
#                values_to = 'value')
# 
# ggplot(combined, aes(x = time, y = value, group = source, color = source)) +
#   geom_line() +
#   facet_wrap( ~ income_type, nrow=2, scales='free')
```

@@

income_equivinc_change_percent <- function(base.dat, int.dat) {
  base.inc <- base.dat %>%
    select(pidp, time, hh_income, equivalent_income, weight) %>%
    group_by(time) %>%
    summarise(base_income = weighted.mean(hh_income, w = weight, na.rm = TRUE),
              base_equiv_income = weighted.mean(equivalent_income, w = weight, na.rm = TRUE))

  combined <- combined %>%
    group_by(time) %>%
    summarise(mean_income = mean(base_income),
              mean_equiv_income = mean(base_equiv_income),
              mean_diff_income = mean(diff_income),
              mean_diff_equiv_income = mean(diff_equiv_income)) %>%
    mutate(percent_change_income = (mean_diff_income / mean_income) * 100,
           percent_change_equiv_income = (mean_diff_equiv_income / mean_equiv_income) * 100) %>%
    select(-mean_income, -mean_equiv_income, -mean_diff_income, -mean_diff_equiv_income) %>%
    pivot_longer(cols = percent_change_income:percent_change_equiv_income,
                 names_prefix = 'percent_change_',
                 names_to = 'variable',
                 values_to = 'percent_change')

  ggplot(combined, aes(x = time, y = percent_change, group = variable, color = variable)) +
    geom_line() +
    geom_hline(yintercept = 0, linetype = 'dashed')
}

income_equivinc_change(base.dat, energy.dat)
income_equivinc_change_percent(base.dat, energy.dat)
#income_equivinc_change(base.dat, wage.dat)
```

@@

```{r}
# ## just look at means in case the means are causing some problems
# base.dat.2 <- base.dat
# base.dat.2$S7_housing_quality2[base.dat.2$S7_housing_quality == 'No to all'] <- 1
# base.dat.2$S7_housing_quality2[base.dat.2$S7_housing_quality == 'Yes to some'] <- 2
# base.dat.2$S7_housing_quality2[base.dat.2$S7_housing_quality == 'Yes to all'] <- 3
# wage.dat.2 <- energy.dat
# wage.dat.2$S7_housing_quality2[wage.dat.2$S7_housing_quality == 'No to all'] <- 1
# wage.dat.2$S7_housing_quality2[wage.dat.2$S7_housing_quality == 'Yes to some'] <- 2
# wage.dat.2$S7_housing_quality2[wage.dat.2$S7_housing_quality == 'Yes to all'] <- 3
# 
# base.hous.mean <- base.dat.2 %>%
#   select(pidp, time, S7_housing_quality2, weight) %>%
#   group_by(time) %>%
#   summarise(mean_housing = weighted.mean(S7_housing_quality2, w = weight, na.rm = TRUE)) %>%
#   mutate(source = 'Baseline')
# wage.hous.mean <- wage.dat.2 %>%
#   select(pidp, time, S7_housing_quality2, weight) %>%
#   group_by(time) %>%
#   summarise(mean_housing = weighted.mean(S7_housing_quality2, w = weight, na.rm = TRUE)) %>%
#   mutate(source = 'EnergyCrisis')
# 
# combined <- rbind(base.hous.mean, wage.hous.mean)
# 
# ggplot(combined, aes(x = time, y = mean_housing, group = source, color = source)) +
#   geom_line() +
#   geom_point()
```

### 2023-09-12 minos/outcomes/equivalent_income_out_batch.Rmd
Some tweaks to equivalent_income_out_batch and tweaked the aggregation to be more verbose
Lots of little things on equivalent income and job_sec module
Changed loneliness to string var from numeric so its easier to understand. Also lots of changes to EI plots

## Income and Equivalent Income

@@

  print(combined2)

@@

## Equivalent Income Change

@@

### By Subpopulation

@@

  ggplot(combined, aes(x = time, y = mean_diff_equiv_income, group = .data[[group.var]], color = .data[[group.var]])) +
    geom_smooth() +
    geom_hline(yintercept = 0, linetype = 'dashed') +
    labs(title = paste0('Equivalent Income change by ', group.var), subtitle = int.name) +
    xlab('Year') +
    ylab('Equivalent Income (£s)')
}

@@

## Percent Change

@@

### All Subgroups

@@

  ggplot(combined, aes(x = time, y = percent_change_equiv_income, group = .data[[group.var]], color = .data[[group.var]])) +
    geom_smooth() +
    geom_hline(yintercept = 0, linetype = 'dashed') +
    labs(title = paste0('Percent change by ', group.var), subtitle = int.name) +
    xlab('Year') +
    ylab('Percent Change')
}

@@

#### Energy Crisis

@@

#### Living Wage

@@

#### All Child

@@

#### Poverty Child

>>>>

# Income and Equivalent Income

@@

@@

# Equivalent Income Change

@@

## By Subpopulation

@@

  ggplot(combined, aes(x = time, y = mean_diff_equiv_income, group = .data[[group.var]], color = .data[[group.var]])) +
    geom_smooth() +
    geom_hline(yintercept = 0, linetype = 'dashed') +
    labs(title = paste0('Absolute change')) +
    xlab('Year') +
    ylab('Equivalent Income (£s)')
}

@@

# Percent Change

@@

## All Subgroups

@@

  ggplot(combined, aes(x = time, y = percent_change_equiv_income, group = .data[[group.var]], color = .data[[group.var]])) +
    geom_smooth() +
    geom_hline(yintercept = 0, linetype = 'dashed') +
    labs(title = paste0('Percent change')) +
    xlab('Year') +
    ylab('Percent Change (%)') +
    scale_fill_discrete(name = 'Income Quintile')
}

@@

### Energy Crisis

@@

### Living Wage

@@

### All Child

@@

### Poverty Child
